Knowledge bases, such as DBpedia, YAGO, and Wikidata, store information about notable entities and their relationships.
A knowledge bases can be considered an instantiation of an ontology.
An ontology  is a formal specification of knowledge consisting of concepts, relations and axioms for validation.
The ontology enables the modeling, sharing and exchange of information, as well as the derivation of new knowledge.
The taxonomy, also called concept or class hierarchy, is a fundamental component of an ontology.
In a taxonomy, classes are arranged hierarchically linked by a subclass-of relation.
Complete taxonomies have exactly one most common class, called the root class.
In Wikidata, the root class is the class \textit{entity}.
The root class is unique, as it is the only class, which has no superclasses in the taxonomy.
However, Wikidata's taxonomy is incomplete in regard to this property.
Orphan classes are classes, which are not the root class, but still do not have superclasses.
Thereby, orphan classes violate the uniqueness of the root class.

The aim of the thesis is the development and evaluation of a method for the classification of orphan classes in the Wikidata taxonomy.
The classification problem poses a particular challenge to the developed solution, since theoretically every other class in the taxonomy represents a possible superclass for a given orphan class.
In Wikidata, the classification problem therefore has over $100,000$ possible superclasses.

The Wikidata taxonomy has a high degree of completeness with regard to the orphan class problem, as only ${\sim} 0.3\%$ of classes are not subclasses of the root class.
Due the automated addition of classes from foreign sources, such as protein and gene databases, only ${\sim} 15\%$ of the taxonomy are relevant to human users.
Therefore, the development and evaluation of the algorithms focuses only on the relevant subset.

The developed hybrid algorithms use word embeddings to represent entities of the knowledge base.
Word embeddings encode the semantic and lexicographical properties of words in text as vectors.
This allows the application of widely used vector-based methods such as regression and neural networks.
The representation of Wikidata statements in triples enables the application of Word2Vec, which maps Wikidata entities to embeddings.
The classification of orphan classes can then be performed using embeddings.
Nearest-neighbors classification, linear projection, and non-linear regression via neural networks were implemented as classifiers.
With an accuracy of $22.83\%$, nearest-neighbor classification is the best performing hybrid algorithm.