
\subsection{Wikidata}
\textbf{TODO: Define entity in Wikidata, how are classes identified, etc.}
\fullcite{Galarraga2016}\\
Wikidata is a open, collaborative and user-driven knowledge base. Its main purpose is to serve as a structural knowledge store for other
Wikimedia projects like Wikipedia.

\subsection{Taxonomy}
\begin{itemize}
\item Ontology\\
	\fullcite{Cimiano2006}\\
	\fullcite{Galarraga2016}
\item Taxonomy\\
	\fullcite{Cimiano2006}\\
	\fullcite{Galarraga2016}\\
\item Connected taxonomy (maybe: consistent taxonomy)
\item Root class
\item Unlinked class
\item Problem statement
\end{itemize}
\textbf{TODO: General notion of ontology and taxonomy}\\
\fullcite{Cimiano2006} defines ontology, which includes the taxonomy, as follows:\\
``
	\begin{definition*}[Ontology]\label{Ontology}
		An \textnormal{ontology} is a structure
		\begin{equation*} 
			\mathcal{O} := (C, \taxon, R, \relsig, \relhier, \mathcal{A}, \attsig, \mathcal{T})
		\end{equation*}
		consisting of
		\begin{itemize}
			\item four disjoint sets $C$, $R$, $\mathcal{A}$, and $\mathcal{T}$ whose elements are called \textnormal{concept identifiers}, 
				\textnormal{relation identifiers}, \textnormal{attribute identifiers} and \textnormal{data types}, respectively,
			\item a semi-upper latice $\taxon$ on $C$ with top element $\rootc$, called \textnormal{concept hierarchy} or \textnormal{taxonomy},	
			\item a function $\relsig: R \rightarrow C^+$ called \textnormal{relation signature},
			\item a partial order $\relhier$ on $R$, called \textnormal{relation hierarchy}, where $r_1 \relhier r_2$ implies $\abs{\relsig (r_1)} = \abs{\relsig (r_2)}$ and
				$\proj{i}{\relsig (r_1)} \taxon \proj{i}{\relsig (r_2)}$, for each $1 \le i \le \abs{\relsig (r_1)}$, and
			\item a function $\attsig : \mathcal{A} \rightarrow C \times \mathcal{T}$, called \textnormal{attribute signature},
			\item a set $\mathcal{T}$ of datatypes such as strings, integers, etc.
		\end{itemize}
	\end{definition*}
	Hereby, $\proj{i}{t}$ is the i-th component of tuple $t$. [...] Further, a semi-upper lattice $\le$ fulfills the following conditions:
	\begin{align*}
		&\forall x x \le x \: \text{(reflexive)} \\
		&\forall x \forall y (x \le y \land y \le x \implies x = y) \: \text{(anti-symmetric)} \\
		&\forall x \forall y \forall z (x \le y \land y \le z \implies x \le z) \: \text{(transitive)}\\
		&\forall x x \le top \: \text{(top element)}\\
		&\forall x \forall y \exists z (z \ge \land z \ge y \land \forall w (w \ge x \land w \ge y \implies w \ge z)) \: \text{(supremum)}
	\end{align*}
	So every two elements have a unique most specific supremum.
''\\

A taxonomy can be modeled as a semi-upper lattice. This induces two important assumptions about the structure and to some degree completeness of the
observed taxonomies. First, there is only one \textit{root class}, top element of the lattice, of which every other class is (transitively) a subclass. Second,
because of the supremum property, the taxonomy is fully connected, which means each class, but the root class, has a superclass.
Wikidata's taxonomy does therefore not fulfill the definition by \fullcite{Cimiano2006}, as it is not fully connected.\\
In the following, new definitions will presented, which attempt to model an incomplete taxonomy based on the already presented data model and structure of Wikidata.
First, basic concepts of graphs will be introduced.
\begin{definition}[Directed graph]\label{directed graph}
	A \textnormal{directed graph} G is an ordered pair $G=(V, E)$, where $V$ is a set of vertices, and $E = \{ (v_1, v_2) \mid v_1, v_2 \in V \}$ 
	is a set of ordered pairs called directed edges, connecting the the vertices.
\end{definition}
\begin{definition}[Predecessor]\label{predecessor}
Let $G=(V, E)$ be a directed graph.
$v_1 \in V$ is a \textnormal{predecessor} of $v_2 \in V$, if there exists an edge so that $(v_1, v_2) \in E$.
Let $v \in V$ be a vertice of G, then $pred(v) = \{ w \mid (w, v) \in E \}$ is the set of predecessors of $v$.
\end{definition}
\begin{definition}[Successor]\label{successor}
$v_1 \in V$ is a \textnormal{successor} of $v_2 \in V$, if there exists an edge so that $(v_2, v_1) \in E$.
Let $v \in V$ be a vertice of G, then $succ(v) = \{ w \mid (v, w) \in E \}$ is the set of successors of $v$.
\end{definition}
\begin{definition}[Walk]\label{walk}
Let $G = (V, E)$ be a directed graph.
A \textnormal{walk} $W$ of length $n \in \mathbb{N}$ is a sequence of vertices $W=(v_1,\ldots, v_n)$ with $v_1,\ldots, 
v_n \in V$,  so that $(v_i, v_{i+1}) \in E \; \forall i=1,\ldots,n-1$.
\end{definition}
\begin{definition}[Cycle]\label{cycle}
A walk $W=(v_1,\ldots, v_n)$ of length $n$ is called a \textnormal{cycle}, if $v_1 = v_n$.
\end{definition}
\begin{definition}[Directed acyclic graph]\label{acyclic directed graph}
A directed graph $G$ is called \textnormal{directed acyclic graph}, if there are no cycles in $G$.
\end{definition}
In Wikidata, a class can have multiple superclasses, therefore a tree structure is not sufficient to model the taxonomy.
However a directed acyclic graph, can model the taxonomy. The acyclic constraint is necessary to ensure that no class is transitively a subclass of itself.
\begin{definition}[Taxonomy]
A \textnormal{taxonomy} $T=(C, S)$ is a directed  acyclic graph, where $C$ is a set of \textnormal{class identifiers}, 
and $S$ is the set of edges, which describe the \textnormal{subclass-of relation}  between two classes. such that $c_1$ is the subclass of $c_2$, if $(c_1, c_2) \in S$.
\end{definition}
\begin{definition}[Subclass-of relation]\label{subclass of}
The transitive binary relation $\subclassof{T}$ on the taxonomy $T=(C, S)$ represents the subclass relationship
of two classes in $T$. Given $c_1, c_2 \in C$, $c_1 \subclassof{T} c_2$, if there is a walk $W=(c_1, \ldots, c_2)$ with length 
$n \ge 1$, which connects $c_1$ and $c_2$. \subclassof{T} is transitive,  $\forall c_1, c_2, c_3 \in C:
c_1 \subclassof{T} c_2 \land c_2 \subclassof{T} c_3 \implies c_1 \subclassof{T} c_3$.
\end{definition}

\subsection{Similarity}
\begin{itemize}
\item semantic similarity e.g. distributional similarity \\
	\fullcite{Lin1998} \\
	\fullcite{Rodriguez2003}
\item geometrical similarity e.g. distance based-similarity, cosine similarity
\end{itemize}

\subsection{Similarity-based classification}
\fullcite{Chen2009}\\
\fullcite{Zhang2015}

\subsection{Text processing}
\begin{itemize}
\item N-Gram \\
	\fullcite{Jurafsky2014}
\item Skip-Gram \\
	\fullcite{Guthrie2006}
\item Counting-based word representations \\ 
	\fullcite{Levy2015}
\item Predictive word representations \\
	\fullcite{Levy2015}
\end{itemize}