\documentclass[f,bachelor,binding,twoside,palatino]{WeSTthesis}
% Please read the README.md file for additional information on the parameters and overall usage of WeSTthesis
\usepackage{import}
\usepackage{preamble}

\author{Alex Baier}

\title{Enrichment of ontological taxonomies using a neural network approach}

\degreecourse{Informatik}

\firstreviewer{Prof. Dr. Steffen Staab}
\firstreviewerinfo{Institute for Web Science and Technologies}

\secondreviewer{Max Mustermann}
\secondreviewerinfo{Institute for Web Science and Technologies}


\begin{document}

% optional: change document language from ngerman to english
\selectlanguage{english}

\maketitle %prints the cover page  an empty page if two-sided print
\pagenumbering{roman}

\tableofcontents

\varclearpage

% list of figures
\listoffigures
\varclearpage

\pagenumbering{arabic}

\section{Introduction}
Motivation. Related work. Solution. Evaluation.

\section{Foundations}

\subsection{Wikidata}
\fullcite{Galarraga2016}

\subsection{Taxonomy}
\begin{itemize}
\item Ontology\\
	\fullcite{Cimiano2009}\\
	Galarraga2016
\item Taxonomy\\
	\fullcite{Cimiano2009}\\
	Galarraga2016
\item Connected taxonomy (maybe: consistent taxonomy)
\item Root class
\item Unlinked class
\item Problem statement
\end{itemize}

\subsection{Similarity}
\begin{itemize}
\item semantic similarity e.g. distributional similarity \\
	\fullcite{Lin1998} \\
	\fullcite{Rodriguez2003}
\item geometrical similarity e.g. distance based-similarity, cosine similarity
\end{itemize}

\subsection{Similarity-based classification}
\fullcite{Chen2009}\\
\fullcite{Zhang2015}

\subsection{Text processing}
\begin{itemize}
\item N-Gram \\
	\fullcite{Jurafsky2014}
\item Skip-Gram \\
	\fullcite{Guthrie2006}
\item Counting-based word representations \\ 
	\fullcite{Levy2015}
\item Predictive word representations \\
	\fullcite{Levy2015}
\end{itemize}

\section{Ontology learning}
General concepts. Classification of considered problem in the task of ontology learning. Related work.\\
\fullcite{Cimiano2009}\\
\fullcite{Wong2012}\\
\fullcite{dAmato16}\\
\fullcite{Petrucci16}\\
\fullcite{Fu2014}

\section{Neural networks}
Notion of neural networks will be introduced.

\subsection{Recursive neural networks for graph representation}
\fullcite{Scarselli2009}
\subsection{Deep neural networks for graph representation}
\fullcite{Cao2016} \\
\fullcite{Raghu2016}
\subsection{Continuous Bag-of-Words}
\fullcite{Mikolov2013}
\subsection{Skip-gram with negative sampling}
\fullcite{Mikolov2013}\\
\fullcite{Levy2015}\\
\fullcite{Goldberg14}

\subsection{Comparison}

\section{Algorithm}

\subsection{Baseline}
\begin{itemize}
\item Hyper parameters
\item Training data
\end{itemize}

\subsection{Supplementing with other resources}
e.g. Wikipedia

\section{Evaluation}

\subsection{Method}
\citeauthor{Dellschaft2006} \cite{Dellschaft2006}

\subsection{Generation of gold standard}

\subsection{Results}

\import{./}{foundations.ltx}


\nocite{*}
\bibliographystyle{plainnat}
\bibliography{bibliography}
\end{document}